humanCdGF_predict_cfu

### 2016-10-14 code/HumanCdGF_predict_cfu.Rmd
remove heatmaps from colonization prediction

### OTUs selected by >`r cutoff`% of models generated by all OTU models 
###### Using the following bacteria: `r taxa_names`

@@

cage_color <- rainbow(length(unique(rf_prediction$cage_id)))
for (i in seq_along(importance_final)) {
    par(mar = c(5,5,2,5))
    partialPlot(rf_n_features, top_colonized_df, names(importance_final)[i],
                xlab='', main=paste(tax_label[i]))
    par(new = T)
    plot(y = top_colonized_df[ , 'log_cfu_med'],
         x = top_colonized_df[ , names(importance_final)[i]], 
         pch = 21, bg = 'gray', xlab = NA, ylab = NA, axes = F)
    axis(side = 4)
    mtext(side = 4, line = 3, 'Log10 CFU')
# To color points by cage - Change pch to 21 and un-comment following lines
#  for(m in seq_along(unique(rf_prediction$cage_id))){
#    cage <- unique(rf_prediction$cage_id)[m]
#    points(y = top_colonized_df[rf_prediction$cage_id %in% cage, 'log_cfu_med'],
#         x = top_colonized_df[rf_prediction$cage_id %in% cage , names(importance_final)[i]], 
#         pch = 21, bg = cage_color[m], xlab = NA, ylab = NA, axes = F)
#  }
}

@@

>>>>

@@

cage_color <- rainbow(length(unique(rf_prediction$cage_id)))
for (i in seq_along(importance_final)) {
    partialPlot(rf_n_features, top_colonized_df, names(importance_final)[i],
                xlab='', main=paste(tax_label[i]))
    par(new = T)
    plot(y = top_colonized_df[ , 'log_cfu_med'],
         x = top_colonized_df[ , names(importance_final)[i]], 
         pch = 21, bg = 'gray', xlab = NA, ylab = NA, axes = F)
    axis(side = 4)
    mtext(side = 4, line = 3, 'Log10 CFU')
# To color points by cage - Change pch to 21 and un-comment following lines
#  for(m in seq_along(unique(rf_prediction$cage_id))){
#    cage <- unique(rf_prediction$cage_id)[m]
#    points(y = top_colonized_df[rf_prediction$cage_id %in% cage, 'log_cfu_med'],
#         x = top_colonized_df[rf_prediction$cage_id %in% cage , names(importance_final)[i]], 
#         pch = 21, bg = cage_color[m], xlab = NA, ylab = NA, axes = F)
#  }
}

@@

### OTUs selected by >`r cutoff`% of models generated by all OTU models 
###### Using the following bacteria: - r taxa_names
